Regular singular Volterra equations on complex domains

### 2023-08-08 reg-sing-volterra.tex
Prove lem:perturbed_volterra

We'll prove this result in Section~\ref{sec:proto-construction-regularity}, Proposition~\ref{prop:asymptotic at infinity}.
\begin{thm}\label{thm:general_volterra}
In the perturbed operator $\volterra = \hardpart +\softpart$ from Section~\ref{setting}, suppose the prototypical part $\hardpart$ satisfies Conditions \eqref{cond:sing}, \eqref{cond:slow}, and \eqref{cond:diag-basic} from Section~\ref{setting:basic}, and the perturbation $\softpart$ satisfies Condition \eqref{cond:eps-lambda} from Section~\ref{setting:perturbed}. Then the Volterra equation
\[f = \volterra f\]
has a unique solution $f$ in the affine subspace
\[ f_0 + \singexpalg{\tau-1+\epsilon}(\Omega) \]
of the function space $\singexpalg{\tau-1}(\Omega)$ defined in Section~\ref{fn-spaces}. Here, $f_0$ is the prototype solution \eqref{eqn:test_solution} from Theorems \ref{thm:basic_volterra}--\ref{thm:proto-growth}, which belongs to the function space $\singexp{\tau-1}{\lambda_0}(\Omega)$. For any $\rho > \tau$, the uniqueness of the solution still holds in the larger affine subspace $f_0 + \singexpalg{\rho-1}(\Omega)$.
\textcolor{RoyalBlue}{Assume $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}, \eqref{cond:slow}} and {\em \eqref{cond:diag-basic}} from Section \ref{setting:basic}. Assume $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}} from Section \ref{setting:perturbed}. Then the Volterra equation 
\[f = \left[ \hardpart + \softpart \right] f\]
admits a unique solution in the affine subspace
\[ f_0 + \singexpalg{\tau-1+\epsilon}(\Omega) \]
of the function space $\singexpalg{\tau-1}(\Omega)$, defined in Section~\ref{fn-spaces}. The function $f_0$ is the prototypical solution of \eqref{eqn:test_solution} and it belongs to the function space $\singexp{\tau-1}{\lambda_0}(\Omega)$.}
\end{thm}
\textcolor{RoyalBlue}{We'll prove this result in Sections~\ref{sec:existence and uniqueness}: using Proposition \ref{prop:smoothing} we show that $\softpart$ maps the prototype solution into a more regular function space. Then the result follows as a consequence of Lemma \ref{lem:perturbed_volterra}.}\par
%--------
This result will follow from a more general result about inhomogeneous equations.
\begin{lemma}\label{lem:perturbed_volterra}
In the perturbed operator $\volterra = \hardpart +\softpart$ from Section~\ref{setting}, suppose the prototypical part $\hardpart$ satisfies Conditions \eqref{cond:sing}, \eqref{cond:slow}, and \eqref{cond:diag-basic} from Section~\ref{setting:basic}, and the perturbation $\softpart$ satisfies Condition \eqref{cond:eps-lambda} from Section~\ref{setting:perturbed}. Suppose we're also given a function $g$, which for some $\rho > \tau$ belongs to the space $\singexpalg{\rho-1}(\Omega)$ defined in Section~\ref{fn-spaces}. Then the inhomogeneous Volterra equation
\[ f = \volterra f + g, \]
has a unique solution $f$ in the space $\singexpalg{\rho-1}(\Omega)$.

@@

\subsection{Continuous inclusions between different $\singexp{\sigma}{\Lambda}(\Omega)$}\label{sec:inclusions}
\begin{prop}
If $\Lambda'\leq\Lambda$, the inclusion map $\singexp{\sigma}{\Lambda'}(\Omega)\hookrightarrow \singexp{\sigma}{\Lambda}(\Omega)$ is continuous.
\end{prop}
\begin{proof}
By definition,
\[ \|f\|_{\sigma,\Lambda}=\sup_{\Omega} |\zeta|^{-\sigma}\,e^{-\Lambda |\zeta|}\, |f|. \]
The norm $\|\cdot\|_{\sigma, \Lambda'}$ is designed to give $|f| \le |\zeta|^\sigma\,e^{\Lambda'|\zeta|}\,\|f\|_{\sigma, \Lambda'}$, which tells us that
\begin{align*}
\|f\|_{\sigma,\Lambda} & \leq \sup_{\Omega} |\zeta|^{-\sigma}\,e^{-\Lambda |\zeta|}\,|\zeta|^\sigma\,e^{\Lambda'|\zeta|}\,\|f\|_{\sigma, \Lambda'}\\
&=\sup_{\Omega} e^{-(\Lambda-\Lambda') |\zeta|}\,\|f\|_{\sigma, \Lambda'}\\
&\leq \|f\|_{\sigma,\Lambda'}.
\end{align*}
In the last step, we use the assumption that $\Lambda' \le \Lambda$.
\end{proof}
As we mentioned in Section~\ref{sec:fn-space-defs}, one might describe $\singexp{0}{\Lambda}(\domain)$ as the space of functions on $\domain$ which are uniformly of exponential type $\Lambda$. Taking the union of these spaces over all $\Lambda \in \R$, we get the space $\singexpalg{0}$ that contains all functions of exponential type. Having continuous inclusions between the subspaces $\singexp{0}{\Lambda}(\domain)$ as $\Lambda$ increases, we can give $\singexpalg{0}$ a meaningful topology: the finest topology that makes all the inclusions $\singexp{0}{\Lambda}(\domain) \hookrightarrow \singexpalg{0}$ continuous.\footnote{In category-theoretic language, $\singexpalg{0}$ is the limit of the family $\singexp{0}{\Lambda}(\domain)$.}
\begin{prop}
    If $\Lambda'<\Lambda$ and $\sigma'>\sigma$, the inclusion map $\singexp{\sigma'}{\Lambda'}(\Omega)\hookrightarrow \singexp{\sigma}{\Lambda}(\Omega)$ is continuous.
\end{prop}

@@

\begin{prop}\label{prop:get-contraction}
Assume $\hardpart$ satisfies {\em Condition \eqref{cond:sing}} and {\em Condition \eqref{cond:diag-basic}}. Assume $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}. For each $\rho > \tau$, we can ensure that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}$ by making $\Lambda$ big enough.
\end{prop}
\begin{rmk}
For the argument, we'll use, ``big enough'' always requires $\Lambda > \lambda_\Delta$, and may require $\Lambda \gg \lambda_\Delta$.
\end{rmk}
First, pick some $\sigma \in (\tau, \rho)$.\footnote{If you'd like, you can fix a choice of $\sigma$---for example, taking $\sigma = \frac{1}{2}(\tau + \rho)$.} By Conditions \eqref{cond:sing} and \eqref{cond:eps-lambda}, we can find a neighborhood $\near \subset \domain$ of $\zeta = 0$ with the property that
\begin{equation}\label{near-limit}
|k(a, a')| \le \frac{\sigma}{|\zeta(a)|}
\end{equation}
for all $a, a' \in \near$ (see Section \ref{sec:bounds on k}). By choosing a small enough positive radius $R$, we can take $\near$ to be the part of $\domain$ where $|\zeta| < R$. Complementarily, let $\far$ be the part of $\domain$ where $R \le |\zeta|$.

@@

We now know that by setting $\Lambda > \textcolor{orange}{2}\lambda_\Delta+ (1/5)^{\rho-1 R^{-1}}$ (in fact $1/5$ can be replaced by any number in $(0,1)$), we can make $|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)|$ as small as we want over all $a \in \far$. This completes our proof of Proposition~\ref{prop:get-contraction}.
\subsection{Existence and uniqueness of the perturbed solution \\ \textit{(proof of Lemma~\ref{lem:perturbed_volterra} and Theorem~\ref{thm:general_volterra})}}\label{sec:existence and uniqueness}

\begin{proof}[Proof of Theorem~\ref{thm:general_volterra}]

%\textcolor{magenta}{[we have to change the definition of $\hardker$ in \S \ref{setting:basic} in $-\frac{q(a')}{p(a)}$.]}

By Theorem \ref{thm:basic_volterra} and \ref{thm:proto-growth} (proved in Section \ref{sec:construction}), there exists a function $f_0\in \singexp{\tau-1}{\lambda_0}(\Omega)$ such that $\hardpart f_0= f_0$. Hence we can solve the Volterra equation

>>>>

We'll prove this result in Section~\ref{sec:proto-construction-regularity}, Proposition~\ref{prop:asymptotic at infinity}.
\begin{thm}\label{thm:general_volterra}
In the perturbed operator $\volterra = \hardpart +\softpart$ from Section~\ref{setting}, suppose the prototypical part $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}}, \eqref{cond:slow}, and \eqref{cond:diag-basic} from Section~\ref{setting:basic}, and the perturbation $\softpart$ satisfies Condition \eqref{cond:eps-lambda} from Section~\ref{setting:perturbed}. Then the Volterra equation
\[f = \volterra f\]
has a unique solution $f$ in the affine subspace
\[ f_0 + \singexpalg{\tau-1+\epsilon}(\Omega) \]
of the function space $\singexpalg{\tau-1}(\Omega)$ defined in Section~\ref{fn-spaces}. Here, $f_0$ is the prototype solution \eqref{eqn:test_solution} from Theorems \ref{thm:basic_volterra}--\ref{thm:proto-growth}, which belongs to the function space $\singexp{\tau-1}{\lambda_0}(\Omega)$. For any $\rho > \tau$, the uniqueness of the solution still holds in the larger affine subspace $f_0 + \singexpalg{\rho-1}(\Omega)$.
\textcolor{RoyalBlue}{Assume $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}, \eqref{cond:slow}} and {\em \eqref{cond:diag-basic}} from Section \ref{setting:basic}. Assume $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}} from Section \ref{setting:perturbed}. Then the Volterra equation 
\[f = \left[ \hardpart + \softpart \right] f\]
admits a unique solution in the affine subspace
\[ f_0 + \singexpalg{\tau-1+\epsilon}(\Omega) \]
of the function space $\singexpalg{\tau-1}(\Omega)$, defined in Section~\ref{fn-spaces}. The function $f_0$ is the prototypical solution of \eqref{eqn:test_solution} and it belongs to the function space $\singexp{\tau-1}{\lambda_0}(\Omega)$.}
\end{thm}
\textcolor{RoyalBlue}{We'll prove this result in Sections~\ref{sec:existence and uniqueness}: using Proposition \ref{prop:smoothing} we show that $\softpart$ maps the prototype solution into a more regular function space. Then the result follows as a consequence of Lemma \ref{lem:perturbed_volterra}.}\par
%--------
This result will follow from a more general result about inhomogeneous equations.
\begin{lemma}\label{lem:perturbed_volterra}
In the perturbed operator $\volterra = \hardpart +\softpart$ from Section~\ref{setting}, suppose the prototypical part $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic} \textcolor{magenta}{[I don't think we actually use \texttt{cond:slow}]} from Section~\ref{setting:basic}, and the perturbation $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}} from Section~\ref{setting:perturbed}. Suppose we're also given a function $g$, which for some $\rho > \tau$ belongs to the space $\singexpalg{\rho-1}(\Omega)$ defined in Section~\ref{fn-spaces}. Then the inhomogeneous Volterra equation
\[ f = \volterra f + g, \]
has a unique solution $f$ in the space $\singexpalg{\rho-1}(\Omega)$.

@@

\subsection{Continuous inclusions between different $\singexp{\sigma}{\Lambda}(\Omega)$}\label{sec:inclusions}
\begin{prop}\label{prop:exp-inclus}
If $\Lambda'\leq\Lambda$, the inclusion map $\singexp{\sigma}{\Lambda'}(\Omega)\hookrightarrow \singexp{\sigma}{\Lambda}(\Omega)$ is continuous.
\end{prop}
\begin{proof}
By definition,
\[ \|f\|_{\sigma,\Lambda}=\sup_{\Omega} |\zeta|^{-\sigma}\,e^{-\Lambda |\zeta|}\, |f|. \]
The norm $\|\cdot\|_{\sigma, \Lambda'}$ is designed to give $|f| \le |\zeta|^\sigma\,e^{\Lambda'|\zeta|}\,\|f\|_{\sigma, \Lambda'}$, which tells us that
\begin{align*}
\|f\|_{\sigma,\Lambda} & \leq \sup_{\Omega} |\zeta|^{-\sigma}\,e^{-\Lambda |\zeta|}\,|\zeta|^\sigma\,e^{\Lambda'|\zeta|}\,\|f\|_{\sigma, \Lambda'}\\
&=\sup_{\Omega} e^{-(\Lambda-\Lambda') |\zeta|}\,\|f\|_{\sigma, \Lambda'}\\
&\leq \|f\|_{\sigma,\Lambda'}.
\end{align*}
In the last step, we use the assumption that $\Lambda' \le \Lambda$.
\end{proof}
As we mentioned in Section~\ref{sec:fn-space-defs}, one might describe $\singexp{0}{\Lambda}(\domain)$ as the space of functions on $\domain$ which are uniformly of exponential type $\Lambda$. Taking the union of these spaces over all $\Lambda \in \R$, we get the space $\singexpalg{0}$ that contains all functions of exponential type. Having continuous inclusions between the subspaces $\singexp{0}{\Lambda}(\domain)$ as $\Lambda$ increases, we can give $\singexpalg{0}$ a meaningful topology: the finest topology that makes all the inclusions $\singexp{0}{\Lambda}(\domain) \hookrightarrow \singexpalg{0}$ continuous.\footnote{In category-theoretic language, $\singexpalg{0}$ is the limit of the family $\singexp{0}{\Lambda}(\domain)$.}
\begin{prop}
    If $\Lambda'<\Lambda$ and $\sigma'>\sigma$, the inclusion map $\singexp{\sigma'}{\Lambda'}(\Omega)\hookrightarrow \singexp{\sigma}{\Lambda}(\Omega)$ is continuous.
\end{prop}

@@

\begin{prop}\label{prop:get-contraction}
Suppose that $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}, and $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}. Then, for each $\rho > \tau$, we can ensure that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}$ by making $\Lambda$ big enough.
\end{prop}
\begin{rmk}
For the argument, we'll use, ``big enough'' always requires $\Lambda > \lambda_\Delta$, and may require $\Lambda \gg \lambda_\Delta$.
\end{rmk}
First, pick some $\sigma \in (\tau, \rho)$.\footnote{If you'd like, you can fix a choice of $\sigma$---for example, taking $\sigma = \frac{1}{2}(\tau + \rho)$.} By Conditions \eqref{cond:sing} and \eqref{cond:eps-lambda}, we can find a neighborhood $\near \subset \domain$ of $\zeta = 0$ with the property that
\begin{equation}\label{near-limit}
|k(a, a')| \le \frac{\sigma}{|\zeta(a)|}
\end{equation}
for all $a, a' \in \near$ (see Section \ref{sec:bounds on k}). By choosing a small enough positive radius $R$, we can take $\near$ to be the part of $\domain$ where $|\zeta| < R$. Complementarily, let $\far$ be the part of $\domain$ where $R \le |\zeta|$.

@@

We now know that by setting $\Lambda > \textcolor{orange}{2}\lambda_\Delta+ (1/5)^{\rho-1 R^{-1}}$ (in fact $1/5$ can be replaced by any number in $(0,1)$), we can make $|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)|$ as small as we want over all $a \in \far$. This completes our proof of Proposition~\ref{prop:get-contraction}.
\subsection{Existence and uniqueness of the perturbed solution \\ \textit{(proof of Lemma~\ref{lem:perturbed_volterra} and Theorem~\ref{thm:general_volterra})}}\label{sec:existence and uniqueness}
\begin{proof}[Proof of Lemma~\ref{lem:perturbed_volterra}]
Choose $\Lambda$ large enough to ensure that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$ and $g$ belongs to $\singexp{\rho-1}{\Lambda}(\Omega)$. Proposition~\ref{prop:get-contraction} guarantees that we can do the former, given our assumptions about $\volterra$ and $\rho$, and the definition of $\singexpalg{\rho-1}(\Omega)$ guarantees that we can also do the latter. Our choice of $\Lambda$ ensures that the affine map $f \mapsto \volterra f + g$ is also a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$, and thus has a unique fixed point in $\singexp{\rho-1}{\Lambda}(\Omega)$ by the contraction mapping theorem.

To see that the fixed point is still unique in the bigger space $\singexpalg{\rho-1}(\Omega)$, first recall from Proposition~\ref{prop:exp-inclus} that we have inclusions $\singexp{\rho-1}{\Lambda'}(\Omega) \hookrightarrow \singexp{\rho-1}{\Lambda}(\Omega)$ for all $\Lambda' \le \Lambda$. Any fixed point in $\singexp{\rho-1}{\Lambda'}(\Omega)$ must map to the unique fixed point in $\singexp{\rho-1}{\Lambda}(\Omega)$ under this inclusion. Next, observe that for any $\Lambda'' \ge \Lambda$, the map $f \mapsto \volterra f + g$ is also a contraction of $\singexp{\rho-1}{\Lambda''}(\Omega)$. The inclusion $\singexp{\rho-1}{\Lambda}(\Omega) \hookrightarrow \singexp{\rho-1}{\Lambda''}(\Omega)$ must send the unique fixed point in the smaller space to the unique fixed point in the larger one. Together, these arguments show that the fixed point is unique in $\singexpalg{\rho-1}(\Omega)$.
\end{proof}
\begin{proof}[Proof of Theorem~\ref{thm:general_volterra}]
%\textcolor{magenta}{[we have to change the definition of $\hardker$ in \S \ref{setting:basic} in $-\frac{q(a')}{p(a)}$.]}
By Theorem \ref{thm:basic_volterra} and \ref{thm:proto-growth} (proved in Section \ref{sec:construction}), there exists a function $f_0\in \singexp{\tau-1}{\lambda_0}(\Omega)$ such that $\hardpart f_0= f_0$. Hence we can solve the Volterra equation
